Staged Abstract Interpreters

### 2019-09-01 paper/70_eval.tex
typos

\paragraph{Implementation and Evaluation Environment}
We implement the abstract interpreters for control-flow analysis, i.e., a
value-flow analysis that computes which lambda terms can be called at each
call-sites in functional languages. With other suitable abstract domains, the
abstract interpreter also can be extended to other analyses. A front-end
desugars Scheme to a small core language that makes the analyzer easy to
implement. We implement two common monovariant 0-CFA-like analysis, one is
equipped with store-widening (0CFA-SW for short), the other does not (0CFA for
short). The store-widened analysis is expected to be faster than the one
without.  Our prototype implementation currently generates Scala code; the
generated Scala code will be compiled and executed on JVM. it is possible to
generate C/C++ code in the future. In the experiments, we implement several
optimizations mentioned in Section \ref{staged_ds}, specifically, the selective
caching scheme and IR-level rewriting rules (for pairs, lists, sets, and maps) exploiting
partially-static data. These optimizations are useful to reduce the size of
generated code.

@@

Figure~\ref{evaluation_result} shows the evaluation result, comparing the
performance improved by staging on the two monovariant CFAs The
\textit{unstaged} and \textit{staged} columns show the median time to finish
the analysis. The column $\frac{\text{unstaged}}{\text{staged}}$ shows the
improvement. The dash - in some cells indicates timeout.  As
expected, the staged version significantly outperforms the unstaged version on
all benchmarks. We observe that simple and homogeneous value domains used in the
benchmark usually leads to better speed-ups.  For 0CFA w/o store-widening, we
observe an average speed-up of ~17x times; for 0CFA w/ store-widening, the
average speed-up is ~7x times.  The \texttt{kcfa-worst-64} benchmark has the most
speed-up among all the tests. Although it has a comparablely large size of AST,
it has a quite simple structure which only involves booleans, functions and
applications. We conjecture that the simple domain and structure allow the
generated code to be efficiently optimized by the JVM. But on the corresponding
0CFA-SW, we do not observe such great speed-up. Due to the complexity of
generated code and next-stage running platform (JVM), we leave the detailed
empirical analysis of which static analysis can benefit more from
specialization as future work.

>>>>

\paragraph{Implementation and Evaluation Environment} We implement the abstract
interpreters for control-flow analysis, i.e., a value-flow analysis that
computes which lambda terms can be called at each call-sites in functional
languages. With other suitable abstract domains, the abstract interpreter also
can be extended to other analyses. A front-end desugars Scheme to a small core
language that makes the analyzer easy to implement. We implement two common
monovariant 0-CFA-like analysis, one is equipped with store-widening (0CFA-SW
for short), the other does not (0CFA for short). The store-widened analysis is
expected to be faster than the one without.  Our prototype implementation
currently generates Scala code; the generated Scala code will be compiled and
executed on JVM. It is possible to generate C/C++ code in the future. In the
experiments, we implement several optimizations mentioned in Section
\ref{staged_ds}, specifically, the selective caching scheme and IR-level
rewriting rules (for pairs, lists, sets, and maps) that exploit
partially-static data. These optimizations are useful to reduce the size of
generated code.

@@

Figure~\ref{evaluation_result} shows the evaluation result, comparing the
performance improved by staging on the two monovariant CFAs The
\textit{unstaged} and \textit{staged} columns show the median time to finish
the analysis. The column $\frac{\text{unstaged}}{\text{staged}}$ shows the
improvement. The dash - in some cells indicates timeout.  As
expected, the staged version significantly outperforms the unstaged version on
all benchmarks. We observe that simple and homogeneous value domains used in the
benchmark usually leads to better speed-ups.  For 0CFA w/o store-widening, we
observe an average speed-up of ~17x times; for 0CFA w/ store-widening, the
average speed-up is ~7x times.  The \texttt{kcfa-worst-64} benchmark has the most
speed-up among all the tests. Although it has a comparably large size of AST,
it has a quite simple structure which only involves booleans, functions and
applications. We conjecture that the simple domain and structure allow the
generated code to be efficiently optimized by the JVM. But on the corresponding
0CFA-SW, we do not observe such great speed-up. Due to the complexity of
generated code and next-stage running platform (JVM), we leave the detailed
empirical analysis of which static analysis can benefit more from
specialization as future work.
